Learning and comparing functional connectomes between populations

### 2012-09-05 paper.tex
Iterate

Different strategies: 
dense/sparse: covering a large fraction of the
brain or not, hard vs soft boundaries.

@@

AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
Personal bias against the AAL.

@@

\paragraph{FMRI-based function definition}
Distinction between activation and rest.
Activation: thresholding GLM maps, or using spheres around the activation
peak.
Rest: ICA-based approaches \cite{kiviniemi2009} XXX: cite Grecius paper.
\cite{varoquaux2011}

@@

Rest: importance of confounds. Filtering + and detrending.

@@

>>>>

Different strategies: 
dense/sparse: covering a large fraction of the
brain or not == tradeoff between functional specificity and covering the
full brain
, hard vs soft boundaries.

@@

AAL \cite{tzourio-mazoyer2002a}, Harvard-oxford, sulci-based atlas.
Personal bias against the AAL, but note that it is widely used because of
SPM toolbox.

@@

\paragraph{FMRI-based function definition}
Distinction between activation and rest.
Activation: thresholding GLM maps, or using spheres around the activation
peak.
Rest: ICA-based approaches \cite{kiviniemi2009} \cite{shirer2012}
\cite{varoquaux2011}

Clustering approaches, \cite{craddock2011}.

@@

Rest: importance of confounds. Filtering + and detrending. Importance of
preprocessing.
Compcorr \cite{behzadi2007}
\cite{chai2011}

@@

Remark that partial correlations consistently have no negative values.
